%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
	{Software Engineering Intern}
	{Apple Inc.}
	{Cupertino, CA, USA}
	{2018 - 2019}
	{
		\begin{cvitems}
			\item {Worked on Swift Package Manager}
			\item {Implemented a new SAT solving based dependency resolution algorithm}
		\end{cvitems}
	}

\cventry
	{Student Assistant}
	{Dresden University of Technology}
	{Dresden, Germany}
	{2013 - present}
	{
		\begin{cvitems}
			\item {Sole maintainer for the iOS app \href{https://navigator.tu-dresden.de/mobile_apps}{\emph{Campus Navigator}} since 2015, a mixed Swift/Objective-C project.}
			\item {Teaching assistant in \emph{Computer Science II} for Mechanical Engineering students teaching C\# and UML.}
			\item {Mentored a first year Computer Science LEGO robotics course.}
			\item {Tutored first semester Computer Science students.}
		\end{cvitems}
	}
	
%\cventry
%	{Personal Project}
%	{\href{https://github.com/kiliankoe/apodidae}{Apodidae}}
%	{}
%	{2017 - present}
%	{
%		\begin{cvitems}
%			\item {Swift command line application to search for available Swift packages on GitHub.}
%		\end{cvitems}
%	}
	
\cventry
	{Personal Project}
	{ParkenDD}
	{}
	{2014 - present}
	{
		\begin{cvitems}
			\item {Implemented the iOS app and backend for ParkenDD, an app that aggregates and shows current available parking spaces in public parking lots for several European cities.}
			\item {\href{https://parkendd.de}{ParkenDD.de}}
		\end{cvitems}
	}
	
\cventry
	{Freelancer}
	{Universitätsklinikum Carl Gustav Carus}
	{Dresden, Germany}
	{2016}
	{
		\begin{cvitems}
			\item {Updated an iOS app used to navigate the university hospital campus to the current iOS SDK.}
			\item {Consulted in what's necessary for a successful iOS app publication.}
		\end{cvitems}
	}
	
\cventry
	{Freelancer}
	{Liefermax GmbH}
	{Dresden, Germany}
	{2015 - 2016}
	{
		\begin{cvitems}
			\item {Collaborated to develop an iPad application to alleviate the job of a beverage deliverer}
			\item {Swift-only project that synced directly with a MSSQL database.}
		\end{cvitems}
	}

	
\cventry
	{Retail Employee}
	{Remus Datentechnik GmbH}
	{Ingolstadt, Germany}
	{2010 - 2012}
	{
		\begin{cvitems}
			\item {Remus Datentechnik GmbH was at the time the only Apple certified Premium Reseller in Ingolstadt.}
			\item {We dealt in all things hard- and software from Apple and other selected vendors besides offering technical support to customers.}
		\end{cvitems}
	}
	
\cventry
	{Journalist}
	{Touchpod.de}
	{}
	{2009 - 2010}
	{
		\begin{cvitems}
			\item {One of the first sites to cover the iPod touch, iPhone and iOS.}
			\item {Several thousand monthly visitors at the time.}
			\item {Wrote articles reviewing Apple hardware and several iOS apps.}
		\end{cvitems}
	}

%---------------------------------------------------------
\end{cventries}
